CSCI 580 : Monte Carlo Path Tracing

### 2015-12-03 paper/paper.tex
paper finished (hopefully)

\documentclass[journal]{IEEEtran}

@@

\begin{description}
  \item[1)] Generate a ray from the camera (position x,y, horizontal and vertical fields of view u,v), passing through the image plane, with $weight = 1$
  \item[2)] Find the point of intersection with the nearest surface
  \item[3)] Determine whether the surface is a light source or not (as indicated by a special coefficients for light emittance)
  \item[3A)] if it is a light source, return $weight * light$
  \item[3B)] if it is not, $weight \mathrel{*}= (Ks+Kd+Ka)/3$ and randomly scatter a new ray according to a probability density function (pdf) approximating its bidirectional refletance distribution function (brdf), and go to step 2
\end{description}

@@

To test our path tracing application, we placed a grey box floating in an environment that is similar to a typical Cornell Box, but with blue and green walls rather than red and green ones. When running the application with different values of $s$ (ray samples from each pixel) and $d$ (recursion depth), we found that the time of execution was linearly related to the amount of samples, which is unsurprising since $s$ controls the number of iterations of a single loop. When increasing $d$ however, the application appears to converge towards a given time. This can be explained by the geometry of the scene having an average number of reflections before hitting a light source. Therefore, beyond this value for d, the application does not take significantly more time to run.

@@

\centering
\includegraphics[width=2.5in]{20s_1d_11m26s}
\caption{20 sets of rays, recursion depth 1, time: 11m26s}
\label{20s_1d_11m26s}

@@

@@

>>>>

\documentclass[12pt,journal]{IEEEtran}

@@

\begin{description}
  \item[1)] Generate a ray from the camera (position x,y, horizontal and vertical fields of view u,v), passing through the image plane, with $weight = 1$
  \item[2)] Find the point of intersection with the nearest surface
  \item[3)] Determine whether the surface is a light source or not (as indicated by a special coefficients for light emittance)
  \item[3A)] if it is a light source, return $weight * light$
  \item[3B)] if not, $weight \mathrel{*}= \frac{Ks+Kd+Ka}{3}$ and randomly scatter a new ray according to a probability density function (pdf) approximating its bidirectional refletance distribution function (brdf), and go to step 2
\end{description}

\newpage

@@

To test our path tracing application, we placed a grey box floating in an environment that is similar to a typical Cornell Box, but with blue and green walls rather than red and green ones. When running the application with different values of $s$ (ray samples from each pixel) and $d$ (recursion depth), we found that the time of execution was linearly related to the amount of samples, which is unsurprising since $s$ controls the number of iterations of a single loop. When increasing $d$ however, the application appears to converge towards a given time. This can be explained by the geometry of the scene having an average number of reflections before hitting a light source. Therefore, beyond this value for d, the application does not take significantly more time to run. Additionally, an increase in $d$ also increases the brightness of the image, since a ray has a higher chance of hitting a light source if it is allowed a greater number of ``bounces'' off surfaces.

@@

\centering
\includegraphics[width=2.6in]{20s_1d_11m26s}
\caption{20 sets of rays, recursion depth 1, time: 11m26s}
\label{20s_1d_11m26s}

@@

\centering
\includegraphics[width=2.6in]{100s_16d_42m10s}
\caption{100 sets of rays, recursion depth 1, time: 42m10s}
\label{1100s_16d_42m10s}

@@

\par
Also, as noted in the result sections, where an increase in $d$ increases brightness, the reflection quantity could be controlled by a random value to keep the shading consistent. This approach is called the Russian Roulette approach, wherein each successive reflected ray diminishes the chance of the next collision producing a reflected ray. This is done by comparing a random value between 0 and 1 to the current weight of the ray, which diminishes with each successive reflection.

\par
Furthermore, for images where $s \ge 10$, fully dark pixels are displayed in a noticeable, somewhat circular pattern. This could be the result of the uniform random reflectance along the semi-circular hemisphere, although there is currently not a definitive answer to why these artifacts appear.
